---
title: "Exam_3"
author: "Stern"
date: "7/8/2021"
output: word_document
---

##1 clear environment

```{r}
rm(list=ls(all=TRUE))
```

##2 Use the WDI package to download data on female labor force participation for all countries for the years 2010-2015. Save the data frame as female_lfp. (Hint: you may will need to Google the indicator.) 
#https://data.worldbank.org/indicator/SL.TLF.CACT.FE.ZS
```{r}
library(WDI)
female_lfp = WDI(country = "all",
                      indicator = c("SL.TLF.CACT.FE.ZS"), # indicator from web 
                      start = 2010, end = 2015, extra = FALSE, cache = NULL)
```

##3 rename variable to flfp
```{r}
library(tidyverse)
female_lfp <- 
  female_lfp %>%
  rename(flfp = SL.TLF.CACT.FE.ZS)
```


##4  Collapse female_lfp by the mean value for flfp for each country. When you do, keep the ISO-2 country code in your data frame as well as the country name. Name your resulting data frame collapsed_flfp.
```{r}
collapsed_flfp <-
  female_lfp %>%
  group_by(country, iso2c) %>%
  summarize(flfp = mean(flfp, na.rm=TRUE))
```

##5 Use R to show which countries have average female force participation rates for the 2010-2015 period that are less than 15%.
```{r}

```


##6. Use R to present a map of the world of using collapsed_flfp, using the viridis color scheme.
#load libraries and set world and border maps
```{r}
library(rio)
library(googlesheets4) 
library(labelled) 
library(data.table)
library(varhandle) 
library(ggrepel) 
library(geosphere) 
library(rgeos)
library(viridis)
library(mapview) 
library(rnaturalearth) 
library(rnaturalearthdata) 
library(devtools)
library(remotes)
library(raster)
library(sp) 
library(sf)
library(Imap)
library(rnaturalearthhires)
library(ggsflabel) 


world <- ne_countries(scale = "large", returnclass = "sf")

world_borders <- st_read("world border shape files/World_Borders.shp")

borders <- st_transform(world_borders, "+proj=longlat +ellps=WGS84 +datum=WGS84")
rm(world_borders)
```


#drop NAs
```{r}
collapsed_flfp <- na.omit(collapsed_flfp, select=c("country", "iso2c",
                                                   "flfp"))
```

#remove non countries and make map
```{r}
collapsed_flfp <- collapsed_flfp[-c(2),]
collapsed_flfp <- collapsed_flfp[-c(2),]
collapsed_flfp <- collapsed_flfp[-c(5),]
collapsed_flfp <- collapsed_flfp[-c(31),]
collapsed_flfp <- collapsed_flfp[-c(32),]
collapsed_flfp <- collapsed_flfp[-c(49:52),]
collapsed_flfp <- collapsed_flfp[-c(57:61),]
collapsed_flfp <- collapsed_flfp[-c(59),]
collapsed_flfp <- collapsed_flfp[-c(73:74),]
collapsed_flfp <- collapsed_flfp[-c(76),]
collapsed_flfp <- collapsed_flfp[-c(77:80),]
collapsed_flfp <- collapsed_flfp[-c(94:97),]
collapsed_flfp <- collapsed_flfp[-c(95),]
collapsed_flfp <- collapsed_flfp[-c(100:102),]
collapsed_flfp <- collapsed_flfp[-c(111:114),]
collapsed_flfp <- collapsed_flfp[-c(128),]
collapsed_flfp <- collapsed_flfp[-c(129:130),]
collapsed_flfp <- collapsed_flfp[-c(125),]
collapsed_flfp <- collapsed_flfp[-c(136:137),]
collapsed_flfp <- collapsed_flfp[-c(150),]
collapsed_flfp <- collapsed_flfp[-c(154:155),]
collapsed_flfp <- collapsed_flfp[-c(158:160),]
collapsed_flfp <- collapsed_flfp[-c(178),]
collapsed_flfp <- collapsed_flfp[-c(185),]
```
```{r}

library(countrycode)
collapsed_flfp$iso2c = countrycode(sourcevar = collapsed_flfp$country,
                           origin = "country.name",
                           destination = "iso2c",
                           warn = TRUE)
collapsed_flfp <- collapsed_flfp[-c(33),]

collapsed_flfp <- 
  collapsed_flfp %>%
  rename(ISO2 = iso2c)

merged_data = left_join(borders, collapsed_flfp, by=c("ISO2"))
setnames(merged_data, "flfp", "FLFP")

final_data <- na.omit(merged_data, select=c("FLFP"))

#make map
final_map = ggplot() +
  geom_sf(data = world) +
  geom_sf(data = final_data, aes(fill=`FLFP`)) + scale_fill_viridis(option = "viridis") +
  ggtitle("Female Labor Force Participation Rate (flfp), 2010-2015") + theme(plot.title = element_text(hjust = 0.5)) +
  theme_void()
final_map
```


##7

South eastern Africa appears to have this cluster if high flfp.



##9. In a Shiny app, what are the three main components and their subcomponents?
The three components are the ui, the server function, and the execute. The ui has a message, the server has an input and output.

##10 Pull this .pdf file from Mike Denly’s webpage. It is a report that Mike Denly and Mike Findley prepared for the US Agency for International Development (USAID). [5 points]
```{r}

library(pdftools)
library(tidyr) 
library(tidytext) 
library(dplyr) 
library(stringr) 
library(ggplot2)

mytext = pdf_text("https://pdf.usaid.gov/pdf_docs/PA00TNMJ.pdf")
print(mytext)
```


##11

```{r}
armeniatext=as.data.frame(mytext, stringsAsFactors = FALSE)
armeniatext$page=c(1:59)
colnames(armeniatext)[which(names(armeniatext) == "mytext")] <- "text" #change column
```

##12

```{r}
armeniatext=armeniatext %>% 
  unnest_tokens(word, text)
data(stop_words)
armeniatext <- armeniatext %>% anti_join(stop_words)
```

##13

```{r}
armenfreq <- armeniatext %>% 
  count(word, sort = TRUE)
head(armenfreq)
```
top 5 = law, corruption, rule, armenia, european


##15
```{r}
library(dplyr)
library(rvest)
hot100exam <- "https://www.billboard.com/charts/hot-100"
hot100exam <- read_html(hot100exam)
```


#16
```{r}
body_nodes <- hot100exam %>% 
  html_node("body") %>% 
  html_children()
body_nodes
body_nodes %>% 
  html_children()

```





